# RNNs are used for modeling Time-Series Data, e.g. Weather Forecasting


# Load relevant libraries for recurrent neural network (rnn)
# Rattle contains inbuilt time-series datasets 
```{r}
library(rattle)
library(rnn)
```

# Weather data of Australian cities
```{r}
data(weatherAUS)
```
```{r}
head(weatherAUS)
dim(weatherAUS)
names(weatherAUS)
```

# Extract "Date" (1st) and "Humidity9am" (14th) columns, and first 3040 rows ('Albury' location)

# Forecast Humdity at 9 am for future dates
```{r}
data <- weatherAUS[1:3040, c(1, 14)]
```
```{r}
summary(data)
# Data contains Nas
```

# Remove NAs
```{r}
data_cleaned <- na.omit(data)
head(data_cleaned)
dim(data_cleaned)
```

```{r}
x <- data_cleaned[, 1] # predictor (date)
y <- data_cleaned[, 2] # response (humidity at 9am)
```

```{r}
head(x)
head(y)
```

```{r}
min(y)
max(y)
```

# ```{r}
# X <- as.matrix(x, nrow = 30)
# Y <- as.matrix(y, nrow = 30)
# ```


# ```{r}
# str(X)
# dim((X))
# str(Y)
# dim(Y)
# ```


# Standardise in the interval 0-1
```{r}
# y_scaled <- (Y - min(Y)) / (max(Y) - min(Y))
y_scaled <- (y - min(y)) / (max(y) - min(y))

y <- t(y_scaled)
```
```{r}
dim(y)
```

```{r}
train <- 1:70
test <- 71:100
```
```{r}
Ymat <- matrix(Y[train])
Xmat <- matrix(as.numeric(X[train]))
```

```{r}
model <- trainr(
  Y = y[train, ],
  X = x[train, ],
  learningrate = 0.05,
  hidden_dim = 16,
  numepochs = 1000
)
```