# Classification of fashion MNIST data
# An MNIST-like dataset of 70,000 28x28 labeled fashion images
# Labels: 0 T-shirt/top, 1 Trouser, 2 Pullover, 3 Dress, 4 Coat, 5 Sandal, 6 Shirt, 7 Sneaker, 8 Bag, 9 Ankle boot
# Each row is a separate image. Column 1 is the class label. Remaining columns are pixel numbers (784 total).
# Each value is the darkness of the pixel (1 to 255)

# Load required libraries
```{r}
require(deepnet)
library(nnet)
```
# Specify global file path, where data set is located
```{r}
file_path <- "E:\\Eskills-Academy-projects\\fashion-mnist\\"
train_file_name <- "fashion-mnist_train.csv"
train_file <- paste(file_path, train_file_name, sep = "")
test_file_name <- "fashion-mnist_test.csv"
test_file <- paste(file_path, test_file_name, sep = "")
```
# Load data
```{r}
f_data <- read.csv(train_file)
```
```{r}
head(f_data)
```
```{r}
str(f_data)
ncol(f_data)
nrow(f_data)
```
# Convert labels from int to factor for Classification
```{r}
f_data$label <- as.factor(f_data$label)
str(f_data)
levels(f_data$label)
```
# Visualize some items
```{r}
sample_4 <- matrix(as.numeric(f_data[4, -1]), nrow = 28, byrow = TRUE)
image(sample_4,
  col = grey.colors(255),
  xaxt = "n", yaxt = "n",
  main = paste("Target:", f_data[4, 1], sep = "")
)
```

```{r}
sample_1 <- matrix(as.numeric(f_data[1, -1]), nrow = 28, byrow = TRUE)
image(sample_1,
  col = grey.colors(255),
  xaxt = "n", yaxt = "n",
  main = paste("Target:", f_data[1, 1], sep = "")
)
```
```{r}
class(f_data$label)
summary(f_data$label)
```

# Training with caret
```{r}
library(caret)
```
# Training and testing data
```{r}
train_index <- createDataPartition(f_data$label, p = 0.75, list = FALSE)
train <- f_data[train_index, ]
test <- f_data[-train_index, ]
```

# Training data: Get Predictors and Response variables 
```{r}
label_column_index <- 1
train_x <- train[, -label_column_index] # predictors
train_y <- train[, label_column_index] # response
```
```{r}
model <- caret::train(
  x = train_x, y = train_y,
  method = "nnet",
  tuneGrid = expand.grid(
    .size = c(5), # Hidden layer with 5 neurons
    .decay = 0.1
  ),
  trControl = trainControl(method = "none"), # No cross validation method
  MaxNWts = 10000,
  maxit = 100
)
```
# Predictions on unseen test data
```{r}
prediction_nn <- predict(model, test, type = "raw")
```
```{r}
head(prediction_nn)
```
# Confusion matrix
```{r}
cm_nn <- table(test$label, prediction_nn)
```
```{r}
cm_nn
```
```{r}
confusionMatrix(test$label, prediction_nn)
```