# Classification of MNIST digits data
# Each grey scale image is vector of size 784 (corresponding to an image matrix of 28*28 pixels of intensity values)
# Lables (1-9, 10->0) are present in first column of the data, rest 2-785 columns are image vector components

# Load required libraries
```{r}
require(deepnet)
library(readr)
library(nnet)
```

# Specify global file path, where data set is located
```{r}
file_path <- "E:\\Eskills-Academy-projects\\"
train_file_name <- "train.csv"
train_file <- paste(file_path, train_file_name, sep = "")
test_file_name <- "test.csv"
test_file <- paste(file_path, test_file_name, sep = "")
```

# Read in the data from the csv files into dataframes train and test
```{r}
train <- read_csv(train_file)
test <- read_csv(test_file)
```
# Get row-counts of training and testing data
```{r}
train_count <- nrow(train)
test_count <- nrow(test)
```
```{r}
col_labels <- 1
# removed first column, which is label
input_x <- as.matrix(train[1:train_count, -col_labels])
# labels in 1st column
input_y <- as.matrix(train[1:train_count, col_labels])
str(input_y)
output_x <- as.matrix(test[1:test_count, ])
```

# Sample data representation
```{r}
rotate <- function(x) t(apply(x, 2, rev))
marg <- 4
par(mfrow = c(2, 3), mar = c(marg, marg, marg, marg))
for (i in 1:6) {
  image(
    rotate(matrix(unlist(train[i, -1]),
      nrow = 28, ncol = 28, byrow = TRUE
    )),
    col = grey.colors(10, rev = TRUE)
  )
}
```

# Explore data
```{r}
head(train)
```
# Convert labels to factors, and check levels
```{r}
train$label <- as.factor(train$label)
levels(train$label)
```

```{r}
library(caret)
library(nnet)
set.seed(1234)
```
# Create model variable
```{r}
model_nn <- nnet(label ~ .,
  data = train,
  size = 50,
  maxit = 10,
  MaxNWts = 100000,
  decay = 1e-4
)
```

# Make predictions on unseen test data
```{r}
prediction_nn <- predict(model_nn, test, type = "class")
head(prediction_nn)
```


```{r}
rotate <- function(x) t(apply(x, 2, rev))
marg <- 1
par(mfrow = c(2, 3), mar = c(marg, marg, marg, marg))
for (i in 1:6) {
  print(prediction_nn[i])
  image(
    rotate(matrix(unlist(test[i, ]),
      nrow = 28, ncol = 28, byrow = TRUE
    )),
    col = grey.colors(10, rev = TRUE),
    main = paste("prediction:", prediction_nn[i]),
    xaxt = "n",
    yaxt = "n"
  )
}
```