# Binary Classification using Neural Network (NNet)

# Load package for classification and regression training (CARET)
```{r}
require(caret)
```

# Specify global file path, where data set is located
```{r}
file_path <- "E:\\Eskills-Academy-projects\\deepLearning-R-data\\Course-Data\\"
file_name <- "UCI_Credit_Card.csv"
credit_file <- paste(file_path, file_name, sep = "")
```

# Read in the data from the csv file into dataframe credit
```{r}
credit <- read.csv(file = credit_file)
head(credit)
```

# Drop unrequired columns 
```{r}
drops <- c("ID")
df <- credit[, !(names(credit) %in% drops)]
head(df)
```

# Rename long column names in header to shorter ones
```{r}
names(df)[names(df) == "default.payment.next.month"] <- "default"
str(df)
```

# 1 is default and 0 is not default, Recode
```{r}
df$default[df$default == 1] <- "Yes"
df$default[df$default == 0] <- "No"
str(df)
```

# Split data into training and testing datasets
```{r}
set.seed(99)
# 75% data for training
Train <- createDataPartition(df$default, p = 0.75, list = FALSE)
```
```{r}
training <- df[Train, ] # 75% data for training
testing <- df[-Train, ] # 25% data for testing
nrow(training)
nrow(testing)
nrow(df)
```

# Implement cross-validation 
```{r}
fit_control <- trainControl(
  method = "cv",
  number = 10,
  preProcOptions = list(thresh = 0.95),
  classProbs = TRUE,
  summaryFunction = twoClassSummary,
  verboseIter = TRUE
)
```
```{r}
model_nnet <- train(default ~ ., training,
  method = "nnet",
  metric = "ROC",
  preProcess = c("center", "scale"),
  trace = FALSE,
  tuneLength = 10,
  trControl = fit_control
)
```
```{r}
model_nnet
```
```{r}
summary(model_nnet)
```
```{r}
plot((model_nnet))
```

```{r}
pred_nnet <- predict(model_nnet, testing)
# summary(pred_nnet)
# summary(testing$default)
```
# confusionMatrix: How well my predicted values match with the labeled testing data
```{r}
cm_nnet <- caret::confusionMatrix(factor(pred_nnet), factor(testing$default))
```
```{r}
cm_nnet
```

# Variable Importance: Indicates the most important variables in the descending order
```{r}
varImp(model_nnet)
```
```{r}
plot(varImp(model_nnet))
```