# Simple Deep Neural Network (DNN) with package neuralnet
# DNN has 2 or more hidden layers, while ANN has 1 hidden layer

```{r}
library(neuralnet)
library(ISLR)
```

```{r}
data <- College
head(data)
dim(data)
names(data)
str(data)
```

# Get vectors of column-wise maximum and minimum values
```{r}
max_data <- apply(data[, 2:18], 2, max) # maximum value
min_data <- apply(data[, 2:18], 2, min) # minimum value
max_data
min_data
```

# Normalize data
```{r}
data_scaled <- scale(data[, 2:18],
  center = min_data, scale = max_data - min_data
)
```

# Recode the qualitative response variable to 0-1 
```{r}
private <- as.numeric(data$Private) - 1
```

# Combine data
```{r}
data_scaled <- cbind(private, data_scaled)
```
```{r}
head(data_scaled)
```

# Split data into test and train datasets
```{r}
index <- sample(seq_len(nrow(data)), round(0.7 * nrow(data))) # 70% training
train_data <- as.data.frame(data_scaled[index, ])
test_data <- as.data.frame(data_scaled[-index, ])
```
```{r}
# Get a list of all column names
n <- names(train_data)
# LHS of ~ is response, and RHS of ' is predictor'
f <- as.formula(paste("private ~", paste(n[!n %in% "private"], collapse = "+")))
f
```
# A Simple Deep Neural Network (DNN)
```{r}
deep_net <- neuralnet(f,
  data = train_data, hidden = c(5, 3),
  # 5 and 3 neurons in 1st and 2nd hidden layers
  linear.output = FALSE
)
```
```{r}
plot(deep_net)
```
# Make predictions on unseen test data
```{r}
predicted_data <- compute(deep_net, test_data[, 2:18])
print(head(predicted_data$net.result))
```

# Function to round off to 0 or 1
```{r}
predicted_data$net.result <- sapply(
  predicted_data$net.result, round,
  digits = 0
)
```
```{r}
table(test_data$private, predicted_data$net.result)
```

```{r}
library(caret)
confusionMatrix(
  as.factor(test_data$private),
  as.factor(predicted_data$net.result)
)
```