# Multilayer Perceptrons (MLP)

# Load package for Stuttgart Neural Network Simulator 
```{r}
require(RSNNS)
```

# Specify global file path, where data set is located
```{r}
file_path <- "E:\\Eskills-Academy-projects\\deepLearning-R-data\\Course-Data\\"
file_name <- "glassClass.csv"
glass_class_file <- paste(file_path, file_name, sep = "")
```

# Read in the data from the csv file into dataframe d
```{r}
d <- read.csv(file = glass_class_file)
head(d)
str(d)
```

# Change the column 'Type' of type int to type factor with 6 levels for classification
```{r}
d$Type <- as.factor(d$Type)
head(d)
str(d)
```
# Take a sample from data and store it in df
```{r}
df <- d[sample(1:nrow(d), length(1:nrow(d))), 1:ncol(d)]
```

# Assign predictors and response variables to respoective dataframes 
```{r}
df_values <- df[, 1:9] # Predictors
df_targets <- decodeClassLabels(df[, 10]) # Response variable
```
# Split dataset into training and testing 
```{r}
df <- splitForTrainingAndTest(df_values, df_targets, ratio = 0.20)
```
# Normalize the data
```{r}
df <- normTrainingAndTestSet(df)
```

```{r}
str(df)
```
# MLPs are fully connected feed-forward networks
# Create the model variable
```{r}
model <- mlp(df$inputsTrain, df$targetsTrain,
  size = 5,
  learnFuncParams = c(0.1),
  maxit = 50,
  inputsTest = df$inputsTest,
  targetsTest = df$targetsTest
)
```
# Print summary of the model
```{r}
summary(model)
```
# Print weight matrix of the learned model
```{r}
weightMatrix(model)
```
# Plot the iterative training and test error
```{r}
plotIterativeError(model)
```

# Make predictions on the unseen test dataset
```{r}
predictions <- predict(model, df$inputsTest)
```
# Confusion matrix

# For the data used in the training
```{r}
confusionMatrix(df$targetsTrain, fitted.values(model))
```
# for the data used in the test
```{r}
confusionMatrix(df$targetsTest, predictions)
```