# Multiclass classification using neural Network

# Load package 
```{r}
require(nnet)
```

# Load inbuilt data
```{r}
data(iris)
head(iris)
summary(iris)
str(iris)
```

# Fit model
```{r}
fit <- nnet(Species ~ .,
  data = iris,
  size = 4,
  decay = 0.0001,
  maxit = 500
)
```
# Summarize the fit
```{r}
summary(fit)
```
# Make predictions
```{r}
predictions <- predict(fit, iris[, 1:4], type = "class")
```

# Summarize accuracy
```{r}
library(caret)
# Convert the char type predictions to factor type predictions
# for creating confusion matrix
prediction_factor <- factor(predictions)
caret::confusionMatrix(iris$Species, prediction_factor)
```

# Multiclass Classification on real data

# Specify global file path, where data set is located
```{r}
file_path <- "E:\\Eskills-Academy-projects\\deepLearning-R-data\\Course-Data\\"
file_name <- "loanPay.csv"
loan_file <- paste(file_path, file_name, sep = "")
```

# Read in the data from the csv file into dataframe credit
```{r}
loan_data <- read.csv(file = loan_file)
head(loan_data)
summary(loan_data)
```
# Convert the response variable to factor type for classification
```{r}
loan_data$loan_status <- factor(loan_data$loan_status)
summary(loan_data)
```
# Replace NA with 0
```{r}
loan_data[is.na(loan_data)] <- 0
```
# Load only the required features into a data frame
```{r}
name_list <- c(
  "loan_status", "Principal",
  "terms", "age", "education", "Gender", "past_due_days"
)

df <- loan_data[, colnames(loan_data) %in% name_list]
head(df)
summary(df)
```
# Convert other required features with discrete classes to factor varaibles
```{r}
df$education <- factor(df$education)
df$Gender <- factor(df$Gender)
summary(df)
```

# Fit the neural network model
```{r}
fit <- nnet(loan_status ~ .,
  data = df,
  size = 4,
  decay = 0.001,
  maxit = 500
)
summary(fit)
```
# Make predictions
```{r}
predictions <- predict(fit, df[, 2:7], type = "class")
p <- as.data.frame(predictions)
table(predictions, df$loan_status)
```
```{r}
library(caret)
caret::confusionMatrix(factor(predictions), df$loan_status)
```