# Exploratory data analysis
```{r}
data(iris)
names(iris)
summary(iris)
```
# Examine data distribution of a quantitative variable
```{r}
hist(iris$Sepal.Length) # distribution of a variable
```
```{r}
boxplot(iris$Sepal.Length, main = "Summary of iris", xlab = "Sepal Length")
```
```{r}
# Relationship between 2 quantitative variables
plot(iris$Sepal.Length, iris$Sepal.Wid)
```
# Plotting categorical or count variables
```{r}
data(mtcars)
# names(mtcars)
# str(mtcars)
counts <- table((mtcars$gear))
barplot(counts, main = "Cars", xlab = "Number of Gears", horiz = TRUE, col = "red")
```


# Improved data visualization
```{r}
library(ggplot2)
```

# Relation b/2 sepal length and width for 3 different species
```{r}
qplot(Sepal.Length, Petal.Length, data = iris, color = Species)
```
```{r}
qplot(Sepal.Length, Petal.Length,
  data = iris, color = Species, size = Petal.Width,
  xlab = "Sepal Length", ylab = "Petal Length",
  main = "Sepal vs Petal Length in Iris data"
)
```
```{r}
qplot(Sepal.Length, Petal.Length,
  data = iris, color = Species,
  xlab = "Sepal Length", ylab = "Petal Length",
  main = "Sepal vs Petal Length in Iris data",
  geom = "line"
)
```


# Main ggplot functions for visualization
# Format: ggplot(data =, aes(x=, y=, ...)) + geom_xxx()
# aes -> we specify x, y
# geom -> Plot type: e.g. histogram, boxplot
```{r}
ggplot(data = iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point()
```
# Distinguishing between species using color scheme, shapes, sizes
# Using aes in ggplot or in geom_xxx
```{r}
ggplot(data = iris, aes(Sepal.Length, Sepal.Width, shape = Species)) +
  geom_point(aes(color = (Species)))
```
# We can only specify color and shapes on factor variables
# Factor: numbers representing categorical values
# function "factor" turns any number into a qualitative representation
```{r}
str(mtcars)
# Gear can be a categorical variable
# Convert gear(integar) to category using factor functino
```
```{r}
ggplot(mtcars, aes(x = mpg, y = wt, color = factor(gear))) +
  geom_point()
```
# Histograms
```{r}
ggplot(iris, aes(x = Sepal.Length, fill = Species)) +
  geom_histogram()
```
# boxplot
```{r}
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot()
```
# Visualize relationship b/w the different variables for 3 species
```{r}
ggplot(data = iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point() +
  facet_grid(. ~ Species) +
  geom_smooth(method = "lm")
```

